---
title: "In-Class Ex04"
author: "Yap Pin Yaw"
date: "6 May 2023"
date-modified: "`r Sys.Date()`"
execute: 
  echo: true
  eval: true
  warning: false
---

## Load Packages

```{r}
pacman::p_load(rstatix, gt, patchwork, tidyverse, webshot2, ggstatsplot)
```

## Import Data

```{r}
exam_data <- read_csv("data/Exam_data.csv")
```

## Visualising Normal Distribution

If the data is normally distributed, the points in a Q-Q plot will lie on a straight diagonal line. Conversely, if the points deviate significantly from the straight diagonal line, then it's less likely that the data is normally distributed.

::: panel-tabset
## The plot

```{r}
#| echo: false
#| fig-width: 4
#| fig-height: 4
ggplot(exam_data,
       aes(sample=ENGLISH)) +
  stat_qq() +
  stat_qq_line()
```

## The code chunk

```{r}
#| eval: false
#| fig-width: 4
#| fig-height: 4
ggplot(exam_data,
       aes(sample=ENGLISH)) +
  stat_qq() +
  stat_qq_line()
```
:::

::: callout-note
We can see that the points deviate significantly from the straight diagonal line. This is a clear indication that the set of data is not normally distributed.
:::

### Combining Statistical graph and analysis table

::: panel-tabset
## The plot

```{r}
#| echo: false

qq <- ggplot(exam_data,
             aes(sample=ENGLISH)) +
  stat_qq() +
  stat_qq_line()

sw_t <- exam_data %>%
  shapiro_test(ENGLISH) %>%
  gt()

tmp <- tempfile(fileext = '.png')
gtsave(sw_t, tmp)
table_png <- png::readPNG(tmp,native = TRUE)

qq + table_png
```

## The code chunk

```{r}
#| eval: false

qq <- ggplot(exam_data,
             aes(sample=ENGLISH)) +
 stat_qq() +
 stat_qq_line()

sw_t <- exam_data %>%
  shapiro_test(ENGLISH) %>%
  gt()

tmp <- tempfile(fileext = '.png')
gtsave(sw_t, tmp)
table_png <- png::readPNG(tmp,native = TRUE)

qq + table_png
```
:::

## Student T-test using a Histogram for ENGLISH

```{r}
set.seed(1234)

gghistostats(
  data = exam_data,
  x = ENGLISH,
  type = "p",
  test.value = 60,
  xlab = "English scores"
)
```

## Welch test for MATHS

```{r}
ggbetweenstats(
  data = exam_data,
  x = GENDER, 
  y = MATHS,
  type = "p",
  messages = FALSE
)
```
